Figures

### 2019-06-21 figures/07_model-selection.Rmd
add a tp re plot

@@

# dotplot tn hu4 randome effects
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

>>>>

```{r tp_re}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TP model, pasture RE slope") + theme(legend.position = 0)

gg_tp_re
```

@@

# dotplot tn hu4 randome effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)
